Trait pleiotropy of regulatory variants increases with the variety of bound transcription factors, regulated genes and active tissues

### 2022-08-29 ms/ms04_discussion.tex
ENH beta and pval improvements
BUG fixed

@@

I developed a colocalization pipeline based on a pipeline that is public at the eQTL Catalogue Github repository ( \url{https://github.com/eQTL-Catalogue/colocalisation} ).
%
First lead eQTLs with FDR 0.05 in each sample are selected and surrounding eQTL and GWAS variants in a radius of 500 000 nt are retrieved.
%
Colocalization between eQTL and GWAS variants is tested using the "coloc.abf" function of CRAN coloc for each window, each eQTL sample and each GWAS.

>>>>

% TODO Causal variants
% If pleiotropic variants bind more transcription factors and are more frequently annotated with a CRM, then these variants are probably more likely causal variants.

% TODO Relation between eQTL and GWAS and related publications.

@@

My colocalization pipeline was initially based on another pipeline that is at the eQTL Catalogue Github repository ( \url{https://github.com/eQTL-Catalogue/colocalisation} ).
%
First lead eQTLs with FDR 0.05 in each sample are selected and surrounding eQTL and GWAS variants with radius of 500,000 nt (Total window 1,000,000 nt) are retrieved.
%
Colocalization between eQTL and GWAS variants is tested using the "coloc.abf" function of CRAN coloc for each window, each eQTL sample and each GWAS.
